Table

### 2021-03-08 manuscript_science.Rmd
edits: final edits for manuscripts etc

---
title: "Ecosystem size and complexity dictate riverine biodiversity"
output:
  pdf_document:
    latex_engine: xelatex
csl: science.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: references.bib
---

@@

**One sentence summary:** Using theory and empirical analysis of extensive community data, this research provides the first robust evidence that ecosystem size and complexity jointly regulate biodiversity in river networks.

@@

Our theoretical analysis yielded results consistent with our prediction. Ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters $\sigma_h$ is greater than the degree of local environmental noise $\sigma_l$ (**Figure 1A**). The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios. The strength of competition and dispersal processes (dispersal distance and probability) did not change the relationships between $\gamma$ diversity and ecosystem properties (compare panels in **Figures 2 and 3**). Hence, the ecosystem size and complexity are expected to increase $\gamma$ diversity regardless of ecological scenarios.

@@

Despite the substantial difference in fish fauna between the study regions, we found strong support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`). In line with our theoretical predictions, the estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity), and these patterns were consistent across the study regions. In particular, the effect of ecosystem complexity was striking in its magnitude. An average change of $\gamma$ diversity per 0.1 branching probability, which was quantified by average predictive comparisons [@gelmanAveragePredictiveComparisons2007], was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods**): this level of increase in $\gamma$ diversity is equivalent to an increase of `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for estimated average predictive comparisons). These effects remained significant even after controlling for the potential influences of climates and land use patterns (**Table 1**).

@@

While the prevailing evidence supports the importance of ecosystem size in scaling species diversity [@hubbellUnifiedNeutralTheory2001; @triantisIslandSpeciesareaRelationship2012; @iwasakiEvaluatingRelationshipBasinscale2012], ecosystem complexity has not received the attention it deserves. However, the ubiquity of scale-invariant complexity across terrestrial [@turnerLandscapeEcologyTheory2015] and aquatic ecosystems [@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure. Our fundamental findings of the dual control of biodiversity should apply beyond branching ecosystems because ecosystem size and complexity both represent a physical 'template' providing a wide spectrum of niche opportunities for living organisms. Further, the proposed framework may be extended to other aspects of biodiversity; for example, a logical next step is to explore how these ecosystem properties regulate functional diversity [@petcheyFunctionalDiversityFD2002; @suHumanImpactsGlobal2021] and shifts in community assembly processes [@chaseStochasticCommunityAssembly2010]. Recognizing the dual control of biodiversity broadens viable options for spatial planning of protected areas or restoration sites, thereby helping conserve biodiversity from societal demands that threaten it. The generalization of our findings in spatially complex ecosystems represents a frontier for future research.

>>>>

---
title: "Title: Ecosystem size and complexity dictate riverine biodiversity"
output:
  pdf_document:
    latex_engine: xelatex
csl: science.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: references.bib
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
---

@@

**One sentence summary:** This study provides the first evidence that ecosystem size and complexity play comparable roles in regulating biodiversity.

@@

Our theoretical analysis yielded results consistent with our prediction. Ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters $\sigma_h$ is greater than the degree of local environmental noise $\sigma_l$ (**Figure 1A**). The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios. Importantly, the impact of ecosystem complexity was comparable to that of ecosystem size (**Figures 2 and 3**); therefore, they play equally-important roles in regulating biodiversity. The strength of competition and dispersal processes (dispersal distance and probability) did not change the relationships between $\gamma$ diversity and ecosystem properties (compare panels in **Figures 2 and 3**). Hence, the ecosystem size and complexity are expected to increase $\gamma$ diversity regardless of ecological scenarios.

@@

Despite the substantial difference in fish fauna between the study regions, we found strong support for the global model in explaining $\gamma$ diversity (Bayes factor = `r round(fit$gamma$bayes_factor, 1)`). In line with our theoretical predictions, the estimated $\gamma$ diversity increased with increasing watershed area (ecosystem size) and branching probability (ecosystem complexity), and these patterns were consistent across the study regions (**Table 1 and Figure 4**). In particular, the effect of ecosystem complexity was striking in its magnitude. Average predictive comparisons [@gelmanAveragePredictiveComparisons2007] revealed that an expected increase of $\gamma$ diversity per 0.1 branching probability was `r op(ap_est$sim_estimate[2] * 0.1)` $\pm$ `r op(ap_est$sim_se[2] * 0.1)` species (**Materials and Methods** and **Supplementary Text**); this level of increase in $\gamma$ diversity requires `r round(ap_est$sim_estimate[2] * 0.1 / ap_est$sim_estimate[1])` km^2^ in the watershed area (see **Table S7** for the estimated average predictive comparisons). These effects remained significant even after controlling for the potential influences of climates and land use patterns (**Table 1**).

@@

While the prevailing evidence supports the importance of ecosystem size in scaling biodiversity patterns [@hubbellUnifiedNeutralTheory2001; @triantisIslandSpeciesareaRelationship2012; @iwasakiEvaluatingRelationshipBasinscale2012; @saboRoleDischargeVariation2010], ecosystem complexity has not received the attention it deserves. However, the ubiquity of scale-invariant complexity across terrestrial [@turnerLandscapeEcologyTheory2015] and aquatic ecosystems [@rodriguez-iturbeFractalRiverBasins2001] calls for more research embracing the two orthogonal dimensions of the ecosystem's geometric structure. Our fundamental findings of the dual control of biodiversity should apply beyond branching ecosystems because ecosystem size and complexity both represent a physical 'template' providing a wide spectrum of niche opportunities for living organisms. Further, the proposed framework may be extended to other aspects of biodiversity; for example, a logical next step is to explore how these ecosystem properties regulate functional diversity [@petcheyFunctionalDiversityFD2002; @suHumanImpactsGlobal2021] and shifts in community assembly processes [@chaseStochasticCommunityAssembly2010]. Recognizing the dual control of biodiversity broadens viable options for spatial planning of protected areas or restoration sites, thereby helping conserve biodiversity from societal demands that threaten it. The generalization of our findings in spatially complex ecosystems represents a frontier for future research.

### 2021-03-08 supplementary_information_science.Rmd
edits: final edits for manuscripts etc

---
title: |
  | Supplementary Information for:
  | Ecosystem size and complexity dictate riverine biodiversity
author:
- Akira Terui^[Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA]
- Seoghyun Kim\footnotemark[1]
- Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of Minnesota, St. Paul, MN 55108, USA]
- Taku Kadoya^[National Institute for Environmental Studies, Tsukuba, Ibaraki 305-8506, Japan]
- Yusuke Miyazaki^[Shiraume Gakuen College, Kodaira, Tokyo 187-8570, Japan]
output:
  pdf_document:
    latex_engine: xelatex
    toc: yes
    toc_depth: 3
bibliography: references.bib
csl: science.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
---

@@

We developed robust regression models with an M-estimation method to examine the effects of macro-scale drivers on diversity metrics. The robust regression analysis is insensitive to outliers of a response variable; therefore, this methods allows us to account for uncertainties of our diversity estimates (see **Fish community data**). Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $w$, $log_{10}~y_w$, were assumed to follow a normal distribution as $log_{10}~y_w \sim Normal(\mu_w, \sigma^2)$. The parameter $\mu_w$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-transformed branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, the fraction of agricultural land use (logit-transformed), and dam density. Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control their effects statistically. We did not include the fractions of urban and forest land use in the statistical models because these variables were strongly correlated with the fraction of agricultural land use (**Figure S19**). Similarly, we did not use mean elevation in the statistical models because it showed a moderate correlation with air temperature (**Figure S19**). Correlations for other combinations of explanatory variables were weak to moderate.

@@

Longitudinal gradients of local species richness have been extensively studied in rivers, illuminating typical patterns observed in nature. The most common pattern is a downstream increase of local species richness [@mcdowall1996; @mcdowall1998; @rahel1991; @terui2016]. However, recent empirical and theoretical studies also showed 'reversed patterns,' in which local species richness decreases downstream [@bsemer2013; @harvey2018]. We predicted the longitudinal gradient of local species richness to confirm that our simulation scenarios are capable of reproducing the previously observed patterns of local species richness. We considered 32 simulation scenarios comprising four landscape and eight ecological scenarios, as described in the main text (a set of parameters is described in **Table S2**). Under each simulation scenario, we generated 10 branching networks with fixed parameters of ecosystem size ($N_p = 100$) and complexity ($P_b = 0.5$). This results in a total of 320 simulation replicates. In each simulation replicate, we allowed interspecific variation in niche optimum $\mu_i$ and width $\sigma_{niche,i}$ ($\mu_i \sim Unif(-1, 1)$ and $\sigma_{niche,i} \sim Unif(0.1, 1)$, respectively; subscript $i$ represents species) and ran 1400 time steps of metacommunity dynamics. We obtained temporal means of local species richness at each habitat patch for the last 1000 time steps. The first 400 time steps were discarded as initialization and burn-in periods. We removed simulation replicates in which no species established populations over the initial 400 time steps. We evaluated the relationship between local species richness and the number of upstream habitat patches, a proxy for the longitudinal position of a habitat patch.

@@

**Hokkaido, Japan.** We used data from the Hokkaido Freshwater Fish Database HFish [@fukushima2011; @fukushima2007], monitoring data at protected watersheds [@comte2021; @terui2018], and primary data collected by the authors [@miyazaki2016; @terui2016], which collectively cover the entire Hokkaido island. Most data were collected from summer to fall. We screened data through the following procedure:

@@

**Midwest, US.** We assembled fish community data collected by the Iowa Department of Natural Resources [@iowadepartmentofnaturalresources2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources [@illinoisenvironmentalprotectionagency2014], Minnesota Pollution Control Agency [@minnesotapollutioncontrolagency2014], and Wisconsin Department of Natural Resources [@wisconsindepartmentofnaturalresources2018]. These data sets cover most of Upper Mississippi (Hydrologic Unit Code 2 [HUC 2] , region 07, as defined by U.S. Geological Survey and U.S. Department of Agriculture Natural Resources Conservation Service [@u.s.geologicalsurveyandu.s.departmentofagriculturenaturalresourcesconservationservice2013]) and the part of Great Lakes (HUC 2, region 04), Missouri (HUC 2, region 10), and Ohio (HUC 2, region 05). Fish data were collected from summer to fall with electrofishing (backpack, barge-type, or boat-mounted) and supplemental netting at some locations. We screened data through the following procedure:

@@

We evaluated sensitivity of asymptotic species richness (Chao 2 estimator) to sample size (i.e., the number of sampling sites in a watershed). We simulated presence-absence data of species with known values of true species richness $S_{true}$ and the number of sampling sites $N_{site}$. In this simulation, presence of species $i$ at site $x$, $J_{ix}$, was drawn from a Bernoulli distribution as $J_{ix} \sim Bernoulli(p_{i}\kappa_{ix})$ where $p_i$ is the detection probability for species $i$ and $\kappa_{ix}$ is the presence probability of species $i$ at site $x$. Based on the incidence frequency of simulated species $F_i = \sum_{x = 1}^{N_{site}}J_{ix}$, we estimated asymptotic species richness using the iNEXT function in the R package 'iNEXT' [@hsieh2016]. We calculated % bias of estimated asymptotic species richness $S_{est}$:

@@

The average predictive comparison provides an intuitive yet rigorous way to quantify effect sizes for each of explanatory variables in regression models with interactions and/or variable transformations [@gelman2007]. The basic predictive comparison $\delta_u$ is an expected change in $y$ on the original scale per a unit difference of the explanatory variable of interest:

@@

where $E(\cdot)$ is a known function (e.g., exponential), $u$ the input of interest (a value for the explanatory variable of interest), $v$ all the other inputs (a vector in general), $\Theta$ a set of parameters in a regression model. In general, $\delta_u$ depends on $u^{(1)}$ and $u^{(2)}$ (the beginning and end points of the hypothesized change in the explanatory variable of interest), $v$, and $\Theta$. Therefore, Gelman and Pardoe [@gelman2007] defined the *average predictive comparison* $\Delta_u$, the mean value of $\delta_u$ over specified distributions of the inputs and model parameters:

@@

However, directly using the above equation is impractical because estimating $p(u^{(1)}|v)$ and $p(u^{(2)}|v)$ from finite data points is challenging (especially when $v$ is continuous). Instead, we estimated $\Delta_u$ using the following equation proposed by Gelman and Pardoe [@gelman2007]:

@@

which should represent how likely it is for $u$ to transition from $u_i$ to $u_j$ with $v_i$ (note that $v_i$ is in general a vector of explanatory variables for data point $i$). We used the following weighting function based on Mahalanobis distances following Gelman and Pardoe [@gelman2007]:

@@

We estimated $\hat \Delta_u$ for watershed area and branching probability using the estimated coefficients $\hat \xi_k$ of the regression model explaining $\gamma$ diversity. A thousand of vectors of simulated parameters $\Theta_s$ were drawn from normal distributions with means of $\hat \xi_k$ and standard deviations of $\sigma_{\xi, k}$ (the estimated standard errors of parameter $\xi_k$). The estimated average predictive comparisons are $\hat \Delta_{u} = \frac{1}{S} \sum_{s=1}^S \hat \Delta_{u,s}$ where

>>>>

---
title: |
  | Supplementary Materials for:
  | Ecosystem size and complexity dictate riverine biodiversity
author:
- Akira Terui^[Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA]
- Seoghyun Kim\footnotemark[1]
- Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of Minnesota, St. Paul, MN 55108, USA]
- Taku Kadoya^[National Institute for Environmental Studies, Tsukuba, Ibaraki 305-8506, Japan]
- Yusuke Miyazaki^[Shiraume Gakuen College, Kodaira, Tokyo 187-8570, Japan]
output:
  pdf_document:
    latex_engine: xelatex
    toc: yes
    toc_depth: 3
bibliography: references.bib
csl: science.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
---

@@

We developed robust regression models with an M-estimation method to examine the effects of macro-scale drivers on diversity metrics. The robust regression analysis is insensitive to outliers of a response variable; therefore, this method allows us to account for uncertainties of our diversity estimates (see **Fish community data**). Log-transformed diversity metrics ($\alpha$, $\beta$ and $\gamma$ diversity) at watershed $w$, $log_{10}~y_w$, were assumed to follow a normal distribution as $log_{10}~y_w \sim Normal(\mu_w, \sigma^2)$. The parameter $\mu_w$ was related to linear predictors, including log-transformed watershed area (ecosystem size; $log_{10}~WA$), log-transformed branching probability (ecosystem complexity; $log_{10}~P_b$), region (coded as Hokkaido = 0, Midwest = 1; $region$), air temperature, precipitation, the fraction of agricultural land use (logit-transformed), and dam density. Although our primary focus of this analysis is to assess the effects of watershed area and branching probability, we included climate and land use variables to control their effects statistically. We did not include the fractions of urban and forest land use in the statistical models because these variables were strongly correlated with the fraction of agricultural land use (**Figure S19**). Similarly, we did not use mean elevation in the statistical models because it showed a moderate correlation with air temperature (**Figure S19**). Correlations for other combinations of explanatory variables were weak to moderate.

@@

Longitudinal gradients of local species richness have been extensively studied in rivers, illuminating typical patterns observed in nature. The most common pattern is a downstream increase of local species richness [@mcdowallFightingFlowDownstreamupstream1998; @rahelFishAssemblagesHabitat1991; @teruiThreeEcologicalFactors2016]. However, recent empirical and theoretical studies also showed 'reversed patterns,' in which local species richness decreases downstream [@bsemerHeadwatersAreCritical2013; @harveyDisturbanceReversesClassic2018]. We predicted the longitudinal gradient of local species richness to confirm that our simulation scenarios are capable of reproducing the previously observed patterns of local species richness. We considered 32 simulation scenarios comprising four landscape and eight ecological scenarios, as described in the main text (a set of parameters is described in **Table S2**). Under each simulation scenario, we generated 10 branching networks with fixed parameters of ecosystem size ($N_p = 100$) and complexity ($P_b = 0.5$). This results in a total of 320 simulation replicates. In each simulation replicate, we allowed interspecific variation in niche optimum $\mu_i$ and width $\sigma_{niche,i}$ ($\mu_i \sim Unif(-1, 1)$ and $\sigma_{niche,i} \sim Unif(0.1, 1)$, respectively; subscript $i$ represents species) and ran 1400 time steps of metacommunity dynamics. We obtained temporal means of local species richness at each habitat patch for the last 1000 time steps. The first 400 time steps were discarded as initialization and burn-in periods. We removed simulation replicates in which no species established populations over the initial 400 time steps. We evaluated the relationship between local species richness and the number of upstream habitat patches, a proxy for the longitudinal position of a habitat patch.

@@

**Hokkaido, Japan.** In Hokkaido, most data were collected from summer to fall. We screened data through the following procedure:

@@

**Midwest, US.** In the Midwest, the data set covered most of Upper Mississippi (Hydrologic Unit Code 2 [HUC 2] , region 07, as defined by U.S. Geological Survey and U.S. Department of Agriculture Natural Resources Conservation Service [@u.s.geologicalsurveyandu.s.departmentofagriculturenaturalresourcesconservationserviceFederalStandardsProcedures2013]) and the part of Great Lakes (HUC 2, region 04), Missouri (HUC 2, region 10), and Ohio (HUC 2, region 05). Fish data were collected from summer to fall with electrofishing (backpack, barge-type, or boat-mounted) and supplemental netting at some locations. We screened data through the following procedure:

@@

We evaluated sensitivity of asymptotic species richness (Chao 2 estimator) to sample size (i.e., the number of sampling sites in a watershed). We simulated presence-absence data of species with known values of true species richness $S_{true}$ and the number of sampling sites $N_{site}$. In this simulation, presence of species $i$ at site $x$, $J_{ix}$, was drawn from a Bernoulli distribution as $J_{ix} \sim Bernoulli(p_{i}\kappa_{ix})$ where $p_i$ is the detection probability for species $i$ and $\kappa_{ix}$ is the presence probability of species $i$ at site $x$. Based on the incidence frequency of simulated species $F_i = \sum_{x = 1}^{N_{site}}J_{ix}$, we estimated asymptotic species richness using the iNEXT function in the R package 'iNEXT' [@hsiehINEXTPackageRarefaction2016]. We calculated % bias of estimated asymptotic species richness $S_{est}$:

@@

The average predictive comparison provides an intuitive yet rigorous way to quantify effect sizes for each of explanatory variables in regression models with interactions and/or variable transformations [@gelmanAveragePredictiveComparisons2007]. The basic predictive comparison $\delta_u$ is an expected change in $y$ on the original scale per a unit difference of the explanatory variable of interest:

@@

where $E(\cdot)$ is a known function (e.g., exponential), $u$ the input of interest (a value for the explanatory variable of interest), $v$ all the other inputs (a vector in general), $\Theta$ a set of parameters in a regression model. In general, $\delta_u$ depends on $u^{(1)}$ and $u^{(2)}$ (the beginning and end points of the hypothesized change in the explanatory variable of interest), $v$, and $\Theta$. Therefore, Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007] defined the *average predictive comparison* $\Delta_u$, the mean value of $\delta_u$ over specified distributions of the inputs and model parameters:

@@

However, directly using the above equation is impractical because estimating $p(u^{(1)}|v)$ and $p(u^{(2)}|v)$ from finite data points is challenging (especially when $v$ is continuous). Instead, we estimated $\Delta_u$ using the following equation proposed by Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007]:

@@

which should represent how likely it is for $u$ to transition from $u_i$ to $u_j$ with $v_i$ (note that $v_i$ is in general a vector of explanatory variables for data point $i$). We used the following weighting function based on Mahalanobis distances following Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007]:

@@

We estimated $\hat \Delta_u$ for watershed area and branching probability using the estimated coefficients $\hat \xi_k$ of the regression model explaining $\gamma$ diversity. A thousand of vectors of simulated parameters $\Theta_s$ were drawn from normal distributions with means of $\hat \xi_k$ and standard deviations of $\sigma_{\xi, k}$ (the estimated standard errors of parameters $\xi_k$). The estimated average predictive comparisons are $\hat \Delta_{u} = \frac{1}{S} \sum_{s=1}^S \hat \Delta_{u,s}$ where

### 2021-03-08 table.Rmd
edits: final edits for manuscripts etc

stargazer::stargazer(fit$alpha$model, fit$beta$model, fit$gamma$model,
                     header = FALSE,
                     type = "latex",
                     ci = TRUE,
                     title = "Estimated parameters of linear regression models explaining fish species richness in Hokkaido (Japan) and the Midwest (US) regions. The 95\\% confidence intervals are shown in parenthesis. Response variables were log-10 transformed. Climate and land use variables (air temperature, precipitation, logit fraction of agriculture, dam density) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one prior to the analysis.",
                     covariate.labels = c("$log_{10}$ Watershed area",
                                          "$log_{10}$ Branching probability",
                                          "Region (Midwest vs. Hokkaido)",
                                          "Air temperature",
                                          "Precipitation",
                                          "Logit fraction of agriculture",
                                          "Dam density",
                                          "Intercept"),
                     single.row = FALSE,
                     digits = 2,
                     dep.var.caption  = "Response variable",
                     dep.var.labels.include = FALSE,
                     column.labels = c("$\\alpha$ diversity", "$\\beta$ diversity", "$\\gamma$ diversity"),
                     keep.stat = c("rsq"),
                     model.numbers = FALSE)

>>>>

stargazer::stargazer(fit$alpha$model, fit$beta$model, fit$gamma$model,
                     header = FALSE,
                     type = "latex",
                     title = "Estimated parameters of robust regression models explaining fish species richness in Hokkaido (Japan) and the Midwest (US). The standard errors are shown in parenthesis. Response variables were log-10 transformed. Climate and land use variables (air temperature, precipitation, logit fraction of agriculture, dam density) are deviations from the regional averages and were standardized to a mean of zero and a standard deviation of one prior to the analysis.",
                     covariate.labels = c("$log_{10}$ Watershed area",
                                          "$log_{10}$ Branching probability",
                                          "Region (Midwest vs. Hokkaido)",
                                          "Air temperature",
                                          "Precipitation",
                                          "Logit fraction of agriculture",
                                          "Dam density",
                                          "Intercept"),
                     single.row = FALSE,
                     digits = 2,
                     dep.var.caption  = "Response variable",
                     dep.var.labels.include = FALSE,
                     column.labels = c("$\\alpha$ diversity", "$\\beta$ diversity", "$\\gamma$ diversity"),
                     keep.stat = c("rsq"),
                     model.numbers = FALSE)
